The Effects of weather on maize yield: New evidence from Kenya

### 2019-01-15 writing/draft4/draft21.tex
tables jackknife

\begin{center}
\begin{threeparttable}
\caption{\label{CVsc}Cross validation: Mean absolute prediction error scaled by IQR}
% files Rcodes/crossvalidation/compareJustTotals.R; Rcodes/crossvalidation/MAPE_ASAL.R;  Rcodes/crossvalidation/MAPE_nonASAL.R  
\begin{indented}
\item[]
\begin{tabular}{@{}lccc}
\\[-1em]
\br
\\[-1em]
\textbf{Sample:}&\textbf{All covariates}&\textbf{Only seasonal}&\textbf{Naive forecast}\\
\hline
{All counties}& $0.3811$&$0.3889$&$0.4277$\\
{ASAL}& $0.5300$&$0.5342$&$0.5835$\\
{non-ASAL}&  $0.2845$&$0.3858$&$0.4510$\\
\br
\end{tabular}
\begin{tablenotes}
\begin{footnotesize}
    \item \textit{Notes:} The coefficient of determination from generalised linear mixed-effects models. The statistic is based on \cite{Nakagawa2013}.  \\
        \begin{adjustwidth}{1cm}{}
    \item[a] The marginal $R^2$ is interpreted as the variance explained by the fixed effects
  \item[b] The conditional $R^2$ is explained by both fixed affects and random effects (in our case by fixed effects and random intercepts)
     \end{adjustwidth}
     \end{footnotesize}
\end{tablenotes}

\begin{center}
\begin{threeparttable}
\caption{\label{CV}Cross validation: Mean absolute prediction error}
% files Rcodes/crossvalidation/compareJustTotals.R; Rcodes/crossvalidation/MAPE_ASAL.R;  Rcodes/crossvalidation/MAPE_nonASAL.R  
\begin{indented}
\item[]
\begin{tabular}{@{}lccc}
\\[-1em]
\br
\\[-1em]
\textbf{Sample:}&\textbf{All covariates}&\textbf{Only seasonal}&\textbf{Naive forecast}\\
\hline
{All counties}& $0.3599$&$0.3673$&$0.4040$\\
{ASAL}& $0.134$&$0.353$\\
{non-ASAL}&  $0.153$&$0.436$\\
\br
\end{tabular}
\begin{tablenotes}
\begin{footnotesize}
    \item \textit{Notes:} The coefficient of determination from generalised linear mixed-effects models. The statistic is based on \cite{Nakagawa2013}.  \\
        \begin{adjustwidth}{1cm}{}
    \item[a] The marginal $R^2$ is interpreted as the variance explained by the fixed effects
  \item[b] The conditional $R^2$ is explained by both fixed affects and random effects (in our case by fixed effects and random intercepts)
     \end{adjustwidth}
     \end{footnotesize}
\end{tablenotes}

\begin{itemize}
\color{blue}
\item If we get the yield data for the period from $2015$ onwards: Out of sample predictions and comparison with the real data
\end{itemize}

\color{black}

@@

\section*{References}

\bibliography{referencesFS}

>>>>

\begin{center}
\begin{threeparttable}
\caption{\label{CVsc}Cross validation: Mean absolute prediction error divided by IQR}
% files Rcodes/crossvalidation/compareJustTotals.R; Rcodes/crossvalidation/MAPE_ASAL.R;  Rcodes/crossvalidation/MAPE_nonASAL.R  
\begin{indented}
\item[]
\begin{tabular}{@{}lccc}
\\[-1em]
\br
\\[-1em]
\textbf{Sample:}&\textbf{All covariates}&\textbf{Only seasonal}&\textbf{Naive forecast}\\
\hline
{All counties}&$0.3811$&$0.3889$&$0.4277$\\
{ASAL}&$0.5300$&$0.5342$&$0.5835$\\
{non-ASAL}&$0.3858$&$0.4043$&$0.4510$\\
\br
\end{tabular}
\end{indented}
\end{threeparttable} 
\end{center}
\vspace{1cm}

@@

\begin{center}
\begin{threeparttable}
\caption{\label{CV}Cross validation: Mean absolute prediction error}
% files Rcodes/crossvalidation/compareJustTotals.R; Rcodes/crossvalidation/MAPE_ASAL.R;  Rcodes/crossvalidation/MAPE_nonASAL.R  
\begin{indented}
\item[]
\begin{tabular}{@{}lccc}
\\[-1em]
\br
\\[-1em]
\textbf{Sample:}&\textbf{All covariates}&\textbf{Only seasonal}&\textbf{Naive forecast}\\
\hline
{All counties}&$0.3599$&$0.3673$&$0.4040$\\
{ASAL}&$0.4352$&$0.4385$&$0.4790$\\
{non-ASAL}&$0.2715$&$0.2845$&$0.3173$\\
\br
\end{tabular}
\end{indented}
\end{threeparttable} 
\end{center}
\vspace{1cm}

\section*{References}
\bibliography{referencesFS}
